### 2021-02-10 docs/manuscript/PLOS-MSc-Thesis.tex
Implement new figures in TIFF

\begin{figure}[!h]
%  \centering
 \includegraphics[width=\textwidth]{figures/metodos/fig_1}
    \caption{\bf Modelling of GRNs.}
    (A) GRN represented as a directed graph with activation (blue arrows) and
    inhibition (red arrows) interactions. Black circles
    tagged with a \textbf{M} represent the morphogen; \textbf{A}, \textbf{B} and
    \textbf{C} represent genes in the network.
    (B) The same GRN represented as an adjacency matrix in which positive values
    represent activation, negative ones represent inhibition and
    zeros represent no interaction.
    (C) Morphogenetic field. In our model the field was composed of a linear
    array of 30 isogenic cells and a morphogen gradient concentration described
    by an exponential decay function. Horizontal arrows between cells represent
    diffusion of gene products between adjacent cells. Optimal gene expression
    pattern is shown top right.
    (D) Spatiotemporal expression profile of a GRN.
 \label{fig:model}
\end{figure}

@@

 \item{\bf Evaluate fitness by comparing the GRN phenotype with the optimal
 phenotype (Fig~\ref{fig:exp-pattern}).} In order to compute the fitness
 function for each GRN we used three different filters. The first filter
 assesses whether the expression profile of the output node reaches a
 quasi-steady state:
 \begin{equation}
  S_{filter} = \left( \frac{1}{I \cdot N}\right) \sqrt{\sum_{i=1}^{I=3}
  \sum_{n=1}^{N=30} ([G]_n^i(t=500) - [G]^i_n(t=250))^2}.
 \end{equation}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/distribution_most_abundant_topologies}
 \caption{\bf Distribution of abundances of network topologies.}
 Most frequent network topologies shown in the grid contain the I3-FFL network
 motif. Topologies are numbered in order of decreasing abundance. The number of
 GRNs belonging to each network topology is presented below topology number.
 Note that network topology number 9 produces the striped phenotype using a
 two-node GRN.
 \label{fig:distopol}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/grafo-hamming-15-nodes-inhibition-bar}
 \caption{\bf Neutral network.}
 This graph shows network topologies connected by one mutational step. Most
 abundant network topologies are shown as black nodes. All nodes with the same
 color belong to a cluster of nodes more connected between them than with other
 nodes in the graph.
 \label{fig:neutral-network}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/vertex_degree_dist-abundance_vs_node_degree}
 \caption{\bf Node degree in the neutral network.}
 (A) Histogram of vertex degree distribution in the neutral network.
 (B) Scatter plot of Topology abundance vs. Node degree in the neutral
 network.
 \label{fig:deg-dist}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=\textwidth]{figures/results/hamming-2pasos}
 \caption{\bf Network of topologies separated by two mutational steps.}
 The network shows that all the topologies are connected by two or less
 mutational steps, except for topology number 420 (big red circle). Big black
 circles correspond to the 15 topologies with higher abundance.
 \label{fig:2neut-net}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/abundance-robustness-complexity-index}
 \caption{\bf Relationship between Abundance and robustness and complexity
 index.} (A) Abundance vs. Robustness. The robustness of each topology was
 calculated as the number of perturbations in which the fitness was greater or
 equal to 0.95 with respect to the total of perturbations performed.
 (B) Abundance vs. Complexity index. Each point in the plot represents one of
 the 714 network topologies.
 \label{fig:ab-rob}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/clustering_of_grns_and_topologies}
 \caption{\bf Clustering of expression profiles and topologies.}
 (A) Clustering of spatiotemporal expression profiles obtained by
 neighbor joining. (B) Clustering of network topologies. Blue circles
 correspond to topologies that contain the I3-FFL network motif.
 \label{fig:clustering}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/topol-9}
 \caption{\bf Expression dynamics of topology 9.}
 A: Network topology number 9. B: Spatiotemporal expression profile of a GRN
 with topology 9.
 \label{fig:topol9}
\end{figure}

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Relevant subgraphs present in the set of GRNs.}
%Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Dynamics of expression of topology number 9.}

\paragraph*{S3 Fig.}
\label{S3_Fig}
{\bf Most GRNs reach the steady state before 250 time steps.}
GRN number 660 displaying the topology number 33 (A) and its spatiotemporal
expression profile (B).

\paragraph*{S4 Fig.}
\label{S4_Fig}
{\bf Bridge topologies in the neutral network.}
%
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
%
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

>>>>

\begin{figure}[!h]
%  \centering
 \includegraphics[width=\textwidth]{figures/metodos/Fig1}
    \caption{\bf Modelling of GRNs.}
    (A) GRN represented as a directed graph with activation (blue arrows) and
    inhibition (red arrows) interactions. Black circles
    tagged with a \textbf{M} represent the morphogen; \textbf{A}, \textbf{B} and
    \textbf{C} represent genes in the network.
    (B) The same GRN represented as an adjacency matrix in which positive values
    represent activation, negative ones represent inhibition and
    zeros represent no interaction.
    (C) Morphogenetic field. In our model the field was composed of a linear
    array of 30 isogenic cells and a morphogen gradient concentration described
    by an exponential decay function. Horizontal arrows between cells represent
    diffusion of gene products between adjacent cells. Optimal gene expression
    pattern is shown top right.
    (D) Spatiotemporal expression profile of a GRN.
 \label{fig:model}
\end{figure}

@@

 \item{\bf Evaluate fitness by comparing the GRN phenotype with the optimal
 phenotype (Fig~\ref{fig:model}C).} In order to compute the fitness
 function for each GRN we used three different filters. The first filter
 assesses whether the expression profile of the output node reaches a
 quasi-steady state:
 \begin{equation}
  S_{filter} = \left( \frac{1}{I \cdot N}\right) \sqrt{\sum_{i=1}^{I=3}
  \sum_{n=1}^{N=30} ([G]_n^i(t=500) - [G]^i_n(t=250))^2}.
 \end{equation}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig2}
 \caption{\bf Distribution of abundances of network topologies.}
 Most frequent network topologies shown in the grid contain the I3-FFL network
 motif. Topologies are numbered in order of decreasing abundance. The number of
 GRNs belonging to each network topology is presented below topology number.
 Note that network topology number 9 produces the striped phenotype using a
 two-node GRN.
 \label{fig:distopol}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig3}
 \caption{\bf Neutral network.}
 This graph shows network topologies connected by one mutational step. Most
 abundant network topologies are shown as black nodes. All nodes with the same
 color belong to a cluster of nodes more connected between them than with other
 nodes in the graph.
 \label{fig:neutral-network}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig4}
 \caption{\bf Node degree in the neutral network.}
 (A) Histogram of vertex degree distribution in the neutral network.
 (B) Scatter plot of Topology abundance vs. Node degree in the neutral
 network.
 \label{fig:deg-dist}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=\textwidth]{figures/results/Fig5}
 \caption{\bf Network of topologies separated by two mutational steps.}
 The network shows that all the topologies are connected by two or less
 mutational steps, except for topology number 420 (big red circle). Big black
 circles correspond to the 15 topologies with higher abundance.
 \label{fig:2neut-net}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig6}
 \caption{\bf Relationship between Abundance and robustness and complexity
 index.} (A) Abundance vs. Robustness. The robustness of each topology was
 calculated as the number of perturbations in which the fitness was greater or
 equal to 0.95 with respect to the total of perturbations performed.
 (B) Abundance vs. Complexity index. Each point in the plot represents one of
 the 714 network topologies.
 \label{fig:ab-rob}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig7}
 \caption{\bf Clustering of expression profiles and topologies.}
 (A) Clustering of spatiotemporal expression profiles obtained by
 neighbor joining. (B) Clustering of network topologies. Blue circles
 correspond to topologies that contain the I3-FFL network motif.
 \label{fig:clustering}
\end{figure}

@@

\begin{figure}[!h]
 \includegraphics[width=\textwidth]{figures/results/Fig8}
 \caption{\bf Expression dynamics of topology 9.}
 A: Network topology number 9. B: Spatiotemporal expression profile of a GRN
 with topology 9.
 \label{fig:topol9}
\end{figure}

@@

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.

\paragraph*{S1 Fig.}
\label{S2_Fig}
{\bf Dynamics of expression of topology number 9.}

\paragraph*{S2 Fig.}
\label{S3_Fig}
{\bf Most GRNs reach the steady state before 250 time steps.}
GRN number 660 displaying the topology number 33 (A) and its spatiotemporal
expression profile (B).

\paragraph*{S3 Fig.}
\label{S4_Fig}
{\bf Bridge topologies in the neutral network.}

\paragraph*{S4 Fig.}
\label{S1_Fig}
{\bf Relevant subgraphs present in the set of GRNs.}
